---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ggrasp

gg and R and sp

This is the "vector" version of tabularaster. 

- convert to gris normalized

```{r}
library(ggrasp)
library(tibble)
library(tidyr)
library(gris)
data(holy_poly)
spdata <- spbabel::sp(holy_poly, attr_tab = tibble(object_ = 1:3, mydat = c("a", "b", "c")))

x <- spdata
br <- gris(x)  ## gris

pr1 <- primitives1D(br) ## edges
pr2 <- primitives2D(pr1) ## triangles


```

Write analogy to gggeom to have doubly nested tables. 

```{r}
ggg <- nest(spdata)
plot(ggg, col = rainbow(nrow(ggg), alpha = 0.5))
```

Use this basis to build data+pslg version atts, 1D primitives, vertices (unique). 


Decompose to just edges. 

```{r}

#edges <- primitives1D()
```

Use that to build 2D primitives. 

Round trip from sp to branches to primitives to sp. Leverage sp/rgeos/rgdal for spatial ops, ggvis for visualization. 

